Appendix A: Stochastic simulations of noisy phenomena

### 2017-11-01 appendixA/appendixA.Rmd
test on drone

---
title: "Appendix A: Stochastic simulations of noisy phenomena"
output: pdf_document
---

```{r}
knitr::opts_chunk$set(message=FALSE, cache = TRUE)
```

```{r libraries}
library(nimble)
library(RcppRoll)
library(regimeshifts) ## devtools::install_github("cboettig/regimeshifts")
library(adaptivetau)
library(tidyverse)

## plot themes, non-essential
library(ggthemes)
library(gridExtra)
#library(hrbrthemes)
#ggplot2::theme_set(hrbrthemes::theme_ipsum())
ggplot2::theme_set(theme_bw())
colours <- ptol_pal()(2)

@@

>>>>

---
title: "Appendix A: Stochastic simulations of noisy phenomena"
output: 
  pdf_document:
    toc: true
bibliography: "../paper/refs.bib"
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE, cache = TRUE, warning = FALSE)
```

```{r libraries}
library(nimble)
library(RcppRoll)
library(regimeshifts) ## devtools::install_github("cboettig/regimeshifts")
library(adaptivetau)
library(tidyverse)
library(ggthemes)
library(gridExtra)
colours <- ptol_pal()(2)
```

```{r include=FALSE}
## plot themes, non-essential. Comment out if theme creates trouble with fonts on your system.
library(hrbrthemes)
library(extrafont)
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts 
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

@@

# References
